\section*{Problem 2}

In this problem we consider the case of one miserly king who has 
demanded a weighing of $N$ coins with the understanding that one coin
is counterfeit and lighter than the others. 
\\
\\
The algorithm to effeciently solve this is as follows:
\begin{enumerate}[noitemsep]
    \item divide coins into three parts $A$, $B$, and $C$. $A$ and $B$
          to be divided into a multiple of three, and the rest are left
          in $C$ 
    \item weigh two of them
    \subitem if $A = B$,  then throw out $A$ and $B$ and keep $C$
    \subitem if $A < B$, then throw out $B$ and $C$ and keep $A$
    \subitem if $B < A$, then throw out a and $C$ and keep $B$
    \item repeat
\end{enumerate} 

In the end, N wasn't divisible by 3, then we will have either 1 or two 
extra to deal with. If there is one extra, then we do two comparisons. 
If there are two extra left then we still do two comparisons.
\\
\\
In the worst case, we do $\lceil \; \log_3 N \; \rceil + 1$ comparisons.
\\
\\
{\centering{\Large \textbf{ALTERNATE}}}
\\
\\
In this problem, we are given $N$ coins and asked to find a lightweight counterfeit amid them. We are instructed that this can only be done by weighing them. The scale we are given indicates the three following cases:
\begin{enumerate}
    \item Side A is heaviest.
    \item Side B is heaviest.
    \item Both sides are of equal weight.
\end{enumerate}

To solve this problem, we divide our coins into problems of size $\ceil[\bigg]{\dfrac{n}{3}}$, and arbitrarily pick two of the three available piles to weigh. There are two possible results of this weighing:
\begin{enumerate}
    \item The two piles are equal in size. Throw them both out; none are fakes. Keep the third pile we didn't weigh, as it must contain a fake.
    \item The two piles are not equal in size. Keep the lightest one, as it contains the fake, and throw out both the heavy one we weighed and the one we didn't weigh.
\end{enumerate}
Repeat this process of dividing up into thirds, keeping discarding the two heavy piles, until only the counterfeit coin remains.
